---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$ \textit{reg_chg}_i = \beta_0 + \beta_1 local_i + \beta_2 poverty_{n,i} + \beta_3 p_n*t_i +\epsilon_i $$

* Describe the population for which you are creating the model.

The population is the Kenyan voting population of 2017. The sample from which
this data was collected includes ~2 mil Kenyan voters.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

```{r}
fit_obj <- stan_glm(data = week_9,
                    reg_chg ~ treatment + poverty_n + treatment*poverty_n,
                    refresh = 0,)

print(fit_obj, detail = FALSE, digits = 4)
```

Intercept: value when all the other values are 0 (so no treatment, median for poverty)
treatmentlocal: effect of being treated on registration change
poverty_n: slope for poverty when treatment is 0 (control)
interaction term: slope for poverty when treatment is 1 (treated)

This tells us that there is more correlation in treatment groups than control groups 
since 0.0155 > 0.0025


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

Even though this data is from 2017, it's reasonable for this data to be applied
in this 2021 scenario. However, if a person gets a SMS reminder in January 2021
to go vote in an August 2022 election, the treatment is not likely to have an effect.
We do not know when the treatment is applied before the 2017 election, so we 
do not know if that could be a confounding factor.

* Describe the ideal Preceptor Table.

A row for each polling station (for all polling stations in Kenya) with data from both 
control and treatment, and the corresponding reg_chg values. In addition, we 
would like to have the 2021 election results

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r sc2}
new_obs <- tibble(treatment = "control", poverty_n = -1.60835093)

pp <- posterior_predict(fit_obj, newdata = new_obs) %>%
  as_tibble() #%>%
  #mutate(all(as.numeric))

ggplot(pp, aes(x = `1`)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) + 
  labs(title = "Posterior Predictive Distribution",
       subtitle = "Registration change at polling station 007/001 under treatment",
       x = "Registration Change",
       y = "Probability") + 
  scale_y_continuous(labels = scales::percent_format()) + 
  scale_x_continuous(labels = scales::percent_format())
```

* Answer the President's question.




## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 

```{r sc3}
new_obs_2 <- tibble(treatment = c("local", "control"),
                    poverty_n = 2)

pe <- posterior_epred(fit_obj, newdata = new_obs_2) %>%
  as_tibble() %>%
  mutate(difference = `1` - `2`)

ggplot(pe, aes(x = difference)) + 
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100)
```



